---
title: "Firms_Producitivity"
author: "Evelyn Sanchez"
date: "2025-10-21"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "/Users/eves/Library/CloudStorage/Dropbox/LATAM_WorldBank/2023/2.Cities and Jobs/1. African cities/2. Data")
```

```{r, echo=FALSE}
library(foreign)
library(haven)
library(readxl)
library(foreign)
library(dplyr)
library(ggplot2)
library(stringr)
library(expss)
library(grid)
library(lattice)
library(survival)
library(Formula)
library(Hmisc)
library(countrycode)
library(tidyverse)
library(WDI)
library(labelled)
library(sandwich)      # robust / clustered VCOV
library(lmtest)        # coeftest, waldtest
library(clubSandwich)  # cluster-robust tests
library(margins)       # marginal effects
library(car)           # deltaMethod
library(splines)       # natural splines
library(mgcv)          # GAM (smooths)
library(ggeffects)   # for tidy predictions
library(stringi)
library(fuzzyjoin)

```

# Set Directories
```{r, echo=FALSE}
dir_out<-"./Output/firms/" 
dir_inter<-"./1_Raw_Informal_micro/Intermediate/"
dir_surveys<-"./1_Raw_Informal_micro/"
dir_harmonized<-"./1_Raw_Informal_micro/Harmonized"
dir_micro<-"./1_Raw_Informal_micro/Intermediate/Micro/"
dir_pop<-"./5_Population/"
dir_frag<- "./2_Fragmentation/"

getwd()
```

```{r}
firms <- read_dta(paste0(dir_inter, "ES_city_productivity2.dta"))

var_label(firms$lprYL_pp) <- "log Labor Productivity (sales per worker) 2009 PPP"
var_label(firms$lprYL) <- "log Labor Productivity (sales per worker) 2009 constant USD"
var_label(firms$d2_ppp_nom) <- "Sales current PPP intl$"
var_label(firms$d2_ppp09) <- "Sales PPP constant 2009 intl$"
var_label(firms$labor_pp)<-"Sales PPP constant 2009 intl$/per worker"


write_dta(firms, paste0(dir_inter, "ES_city_productivity3.dta"))
```

```{r}
#cities matched in the Employment prediction & in WBES
cities_match<-read.csv(paste0(dir_pop,"cities_list.csv"))

firms$year_sur <- str_sub(firms$country, -4)

#get year of survey and country to get density
df <- firms %>% distinct(iso3c, year_sur)

countries<-unique(firms$iso3c)

ghsl<-read_csv(paste0(dir_pop, "GHS_UCDB_THEME_GHSL_GLOBE_R2024A.csv"), locale = locale(encoding = "LATIN1"))
ghsl$GC_CNT_GAD_2025[ghsl$GC_CNT_GAD_2025=="México"] <-"Mexico"

ghsl$iso3c<-countrycode(ghsl$GC_CNT_GAD_2025, "country.name", "iso3c")

ghsl1 <- ghsl %>%
  select(iso3c, ID_UC_G0, GC_UCN_MAI_2025, GC_CNT_GAD_2025, starts_with("GH_XST_D30"))


ghsl1 <- ghsl1 %>%
  rename_with(~ str_remove(.x, "^GH_XST_D30_"), starts_with("GH_XST_D30_"))

ghsl_long <- ghsl1 %>%
  pivot_longer(
    cols = matches("^(19|20)\\d{2}$"),   # columns named 1975, 1980, …, 2025
    names_to   = "year",
    values_to  = "density",
    names_transform = list(year = as.integer)
  ) %>%
  select(iso3c, ID_UC_G0, GC_UCN_MAI_2025, GC_CNT_GAD_2025, year, density) %>%
  arrange(iso3c, ID_UC_G0, year) 

#get population

ghsl_pop <- ghsl%>%
  select(iso3c, ID_UC_G0, GC_UCN_MAI_2025, GC_CNT_GAD_2025, starts_with("GH_POP_TOT"))

ghsl_pop <- ghsl_pop %>%
  rename_with(~ str_remove(.x, "^GH_POP_TOT_"), starts_with("GH_POP_TOT_"))

ghsl_pop_long <- ghsl_pop %>%
  pivot_longer(
    cols = matches("^(19|20)\\d{2}$"),   # columns named 1975, 1980, …, 2025
    names_to   = "year",
    values_to  = "pop_ghsl",
    names_transform = list(year = as.integer)
  ) %>%
  select(iso3c, ID_UC_G0, GC_UCN_MAI_2025, GC_CNT_GAD_2025, year, pop_ghsl) %>%
  arrange(iso3c, ID_UC_G0, year) 

# make sure years are numeric
df <- df %>%
  mutate(year_sur = as.integer(year_sur))

# join by closest year: population
ghsl_closest <- ghsl_long %>%
  inner_join(df, by = "iso3c") %>% 
  mutate(diff = abs(year - year_sur)) %>% 
  group_by(iso3c, ID_UC_G0, year_sur) %>% 
  slice_min(order_by = diff, n = 1, with_ties = FALSE) %>% 
  ungroup()

ghsl_pop <- ghsl_pop_long %>%
  inner_join(df, by = "iso3c") %>% 
  mutate(diff = abs(year - year_sur)) %>% 
  group_by(iso3c, ID_UC_G0, year_sur) %>% 
  slice_min(order_by = diff, n = 1, with_ties = FALSE) %>% 
  ungroup()

names_match<-read.csv(paste0(dir_inter,"correct_names_manual.csv"))

names_match1<-names_match$name_ghsl
colnames(names_match)[colnames(names_match)=="name_ghsl"] <- "GC_UCN_MAI_2025"
names_match <- names_match %>%
  filter(!is.na(GC_UCN_MAI_2025), GC_UCN_MAI_2025 != "")

ghsl_den<-ghsl_closest%>%filter(GC_UCN_MAI_2025 %in% names_match1)
den<-ghsl_den%>%select(GC_UCN_MAI_2025,ID_UC_G0)

ghsl_pop<-ghsl_pop%>%filter(GC_UCN_MAI_2025 %in% names_match1)
pop<-ghsl_pop%>%select(ID_UC_G0, pop_ghsl)

##
den<-left_join(den, names_match, by="GC_UCN_MAI_2025")
den$GC_UCN_MAI_2025<-NULL
ghsl_den<-left_join(ghsl_den, den, by="ID_UC_G0")
ghsl_den<-left_join(ghsl_den, pop, by="ID_UC_G0")
colnames(ghsl_den)[colnames(ghsl_den)=="name"] <- "a3ax"
colnames(ghsl_den)[colnames(ghsl_den)=="year"] <- "year_den_ghsl"
colnames(ghsl_den)[colnames(ghsl_den)=="GC_UCN_MAI_2025"] <- "ghsl_name"

ghsl_den<-ghsl_den%>%select("iso3c", "ID_UC_G0", "ghsl_name", "year_den_ghsl", "density",  "pop_ghsl", "a3ax")
ghsl_den <- ghsl_den[ghsl_den$ID_UC_G0 != "10472", ]


```


```{r}
### IGNORE: Fragmentation data (older version, only used to match city names)

#frag<-read.csv(paste0(dir_frag,"fragmentation_data.csv"))

#frag$city <- sub("^.{4}", "", frag$city)

#write.csv(firm_data, paste0(dir_inter, "frag_correct_names.csv"), row.names = FALSE)
#macth

#ghsl_name<- data.frame(names_match$GC_UCN_MAI_2025)
#colnames(ghsl_name)<-c("name_ghsl")
#frag_name<-data.frame(frag$city)
#colnames(frag_name)<-c("name_frag")
#ghsl_firms <- ghsl_firms %>% distinct(name_ghsl)


#for(i in 1:dim(ghsl_name)[1]) {
# x <- agrep(ghsl_name$name_ghsl[i], frag_name$name_frag,
 #ignore.case=TRUE, value=TRUE,
# max.distance = 0.09, useBytes = TRUE)
 #x <- paste0(x,"")
# ghsl_name$name_frag2[i] <- x
#} 

#matches <- stringdist_join(names_match, frag,
#                           by = c("GC_UCN_MAI_2025" = "city"),
#                           mode = "left",
#                           max_dist = 2, # tune this threshold
#                           method = "lv") # Levenshtein distance
#matches

# 1) Helper to normalize city names safely
#norm_city <- function(x) {
#  x %>%
#    stri_enc_toutf8(is_unknown_8bit = TRUE) %>%      # fix invalid encodings → UTF-8
#    stri_trans_general("Latin-ASCII") %>%            # drop accents (e.g., São → Sao)
#    tolower() %>%
#    stri_trim_both() %>%
#    stri_replace_all_regex("\\s+", " ") %>%          # collapse multiple spaces
#    stri_replace_all_regex("[^a-z0-9 \\-]", "")      # strip odd punctuation (keep hyphens)
#}

# 2) Make cleaned columns on both data frames (don’t overwrite your originals)
#names_match2 <- ghsl_den%>%select(iso3c, ID_UC_G0, ghsl_name)%>%
#  mutate(city_clean = norm_city(ghsl_name))


#frag2 <- frag %>% select(city)%>%
#  mutate(city_clean = norm_city(city))

#matches_raw <- stringdist_join(
#  names_match2, frag2,
#  by = c("city_clean" = "city_clean"),
#  mode = "left",
#  method = "jw",
#  max_dist = 0.18,
#  distance_col = "dist"
#)

#matches <- matches_raw %>%
 # group_by(ghsl_name) %>%
  #slice_min(dist, with_ties = FALSE) %>%
#  ungroup()

#matches$city[matches$ID_UC_G0=="7963"] <- "delhi"


#matches_raw<-matches%>%select(ID_UC_G0, ghsl_name, city)
#frag <- frag %>%
 # mutate(city_clean = norm_city(city))
#colnames(frag)[colnames(frag)=="city"] <- "frag_name"
#colnames(frag)[colnames(frag)=="city_clean"] <- "city"

#matched_raw<-left_join(matches_raw, frag, by="city")

#sum(is.na(matched_raw$shannon))
#46/57

#sum(is.na(matched_raw$city))
#46/45

#add all to firms
#matched_raw<-matched_raw%>%select(ID_UC_G0, shannon, shannon_normalised, batty, batty_normalised)

#ghsl_den2<-left_join(ghsl_den, matched_raw, by="ID_UC_G0")

#sum(is.na(ghsl_den2$shannon))
#merge with firms data



#firms2<-left_join(firms, ghsl_den2, by = c("a3ax", "iso3c"))



#unique(firms2$a3ax)


```
#Join productivity data  with fragmentation 2 (employment clusters data)
#Fragemntation data 
#lasym inv=Job uniformity=values closer to 0 indicate concentrated job distribution and those closer to 1 indicate uniform job spread.
#Batty (spread of clusters)= spatial spread of clusters across the city  
#Shannon (how even clusters are in size)= evenness of cluster size 
```{r}
#get the list with all codes to match
codes<-read.csv(paste0(dir_inter, "FUA_ID_UC.csv"))
#list with the cities matched 
cities_list<-read.csv(paste0(dir_frag, "fragmentation_data_v2.csv"))
cities_list<-cities_list$city
#list with the latest data (including lasym)
frag3<-read.csv(paste0(dir_frag, "fragmentation_data_v3_1.csv"))
frag32<-frag3%>%filter(city %in% cities_list)
fuas<-frag32$eFUA_ID
codes2<-codes%>%filter(eFUA_ID %in%fuas)
#81 cities
frag_84<-left_join(codes2, frag32, by="eFUA_ID")
colnames(frag_84)[colnames(frag_84)=="id_uc_g0"] <- "ID_UC_G0"

new_mesures<-left_join(ghsl_den, frag_84, by="ID_UC_G0")

firms_v4<-left_join(firms, new_mesures, by = c("a3ax", "iso3c"))

firms_v4$region_name<-ifelse(firms_v4$region==1, "SSA", ifelse(firms_v4$region==2, "EAP", ifelse(firms_v4$region==4, "LAC", ifelse(firms_v4$region==5, "MNA", ifelse(firms_v4$region==6, "SAR", NA)))))


####check how many cities
firms1<-firms_v4%>%filter(!is.na(lprYL_pp))
firms1 %>%
  distinct(country, region_name) %>%
 count(region_name, name = "n_cities")

firms1<-firms_v4%>%filter(!is.na(lprYL_pp))
firms1 %>%
  distinct(country, region_name) %>%
 count(region_name, name = "n_cities")

test<-firms1%>%filter(region_name=="EAP")
test%>%distinct(iso3c) #gshl_name
firms1$ghsl_name
###with productivity and density data (18345 FIRMS)
#countries
#EAP	14			
#LAC	13			
#MNA	5			
#SAR	5			
#SSA	26

#cities
#EAP	24			
#LAC	26			
#MNA	18			
#SAR	15			
#SSA	55	

firms1<-firms_v4%>%filter(!is.na(city))
firms1 %>%
  distinct(city, region_name) %>%
 count(region_name, name = "n_cities")

test<-firms1%>%filter(region_name=="EAP")
test%>%distinct(iso3c) #gshl_name
firms1$ghsl_name

### with fragementation data (count if has "city" name)
#countries
#EAP	6			
#LAC	8			
#SAR	3			
#SSA	15

#firms1 %>%
#  distinct(city, region_name) %>%
# count(region_name, name = "n_cities")
#cities
#EAP	8			
#LAC	20			
#SAR	12			
#SSA	36

#number of cities per r

table(firms_v4)
```
#clean space
```{r}
#clean directory
keep <- c("firms", "firms_v4", "firms2", "firms_v4",  "frag", "prod", "prod2", "dir_out", "dir_inter", "dir_pop", "dir_frag", "dir_surveys", "ghsl_den", "ghsl_den2")
rm(list = setdiff(ls(), keep))


colnames(firms_v4)
colnames(firms_v4)[colnames(firms_v4)=="batty"] <- "Batty"
colnames(firms_v4)[colnames(firms_v4)=="shannon"] <- "Shannon"
colnames(firms_v4)[colnames(firms_v4)=="lasym_flipped"] <- "Lasym_inv"
```


#Winsorize variables 
```{r}
firms_v4$id_city<-firms_v4$ID_UC_G0

#Winsorize density 
#firms3<-firms2%>%filter(a3ax!="Abuja")
firms_v4$ln_density <- ifelse(is.finite(firms_v4$density) & firms_v4$density > 0,
                            log(firms_v4$density),
                            NA_real_)
x <- firms_v4$ln_density
qs <- quantile(x, c(0.01, 0.99), na.rm = TRUE)
firms_v4$ln_density_win <- pmin(pmax(x, qs[1]), qs[2])

#Winsorize productivity
x <- firms_v4$lprYL_pp
qs <- quantile(x, c(0.01, 0.99), na.rm = TRUE)
firms_v4$lprYL_pp_win <- pmin(pmax(x, qs[1]), qs[2])
                              
firms_v4$region_name<-ifelse(firms_v4$region==1, "SSA", ifelse(firms_v4$region==2, "EAP", ifelse(firms_v4$region==4, "LAC", ifelse(firms_v4$region==5, "MNA", ifelse(firms_v4$region==6, "SAR", NA)))))
#firms_v4$ln_density_win <- DescTools::Winsorize(firms2$ln_density, probs = c(0.01, 0.99), na.rm = TRUE)

# log population
firms_v4$ln_pop <- ifelse(is.finite(firms_v4$pop_ghsl) & firms_v4$pop_ghsl > 0,
                            log(firms_v4$pop_ghsl),
                            NA_real_)
x <- firms_v4$ln_pop
qs <- quantile(x, c(0.01, 0.99), na.rm = TRUE)
firms_v4$ln_pop_win <- pmin(pmax(x, qs[1]), qs[2])


# log roads

firms_v4$ln_roads <- ifelse(is.finite(firms_v4$road_dens_ghsl) & firms_v4$road_dens_ghsl > 0,
                            log(firms_v4$road_dens_ghsl),
                            NA_real_)
x <- firms_v4$ln_roads
qs <- quantile(x, c(0.01, 0.99), na.rm = TRUE)
firms_v4$ln_roads_win <- pmin(pmax(x, qs[1]), qs[2])

#range(firms_v4$road_dens_ghsl, na.rm = T)


#no EAP or MENA - just to test 
firms5<-firms_v4%>%filter(region_name!="EAP")
firms5<-firms5%>%filter(region_name!="MNA")

#Save data 
write.csv(firms_v4, paste0(dir_out, "Prod_Firms_Fragmenta_complete.csv"), row.names = FALSE)
write.csv(firms5, paste0(dir_out, "Prod_Firms_Fragmenta_complete_noEAP_MNA.csv"), row.names = FALSE)
#Save data 
```

#Check correlations 
```{r}
library(corrplot)
corr_vars <- firms_v4 %>%
  select(lprYL_pp_win, ln_density_win, Shannon, Batty, Lasym_inv, ln_pop_win, ln_roads_win)

corr_matrix <- cor(corr_vars, use = "complete.obs")
png(paste0(dir_out, "correlation_matrix.png"), height = 800, width = 800)
corrplot(corr_matrix, method = "color", type = "upper",
         addCoef.col = "black", tl.col = "black", tl.srt = 45)


png(paste0(dir_out, "correlation_matrix.png"), height = 800, width = 800)
```

# Simple regression firms productivity with density
```{r}
library(modelsummary)
mod_infer1 <- lm(
  lprYL_pp_win ~ ln_density_win + ln_size + ln_age + ln_exp + multi + region_name + sector_MS+ 
    #ln_pop_win+ 
   # ln_roads_win+ 
    iso3c + a14y,
  data = firms_v4,
  weights = w_city_norm,
  na.action = na.exclude
)
cl_vcov <- sandwich::vcovCL(mod_infer1, cluster = ~ id_city, type = "HC1")
coeftest(mod_infer1, vcov = cl_vcov)

# Create modelsummary table
suppressWarnings(
modelsummary(
  list("Log Labor Prod. (sales per worker)" = mod_infer1),
  vcov = cl_vcov,                    # <—— use this, not vcov_iso
  gof_map = c("nobs", "r.squared"),
  coef_omit = "factor(iso3c)|factor(a14y)|factor(region_name)|factor(sector_MS)",
  coef_map = c(
    "ln_density_win"    = "Log Density",
    "ln_pop_win"    = "Log Population",
    "ln_roads_win" = "Road Density",
    "ln_size" = "Log Firm size",
    "ln_age" = "Log age of establishment",
    "ln_exp" = "Log owners experience", 
    "multi" = "Multi establishment"
  ),
  stars = TRUE,
  title = "lprYL_pp_win ~ ln_density_win +  ln_size + ln_age + ln_pop_win+
    ln_exp + multi + factor(region_name) + factor(sector_MS) + 
    + factor(iso3c) + factor(a14y)",
  fmt = 3,
  output = file.path(dir_out, "model_desity_v4_allfirms.html")
))
#ln_pop_win +
#d0 <- firms_v4

#d0$region_name <- factor(d0$region_name)
#d0$sector_MS   <- factor(d0$sector_MS)
#d0$iso3c       <- factor(d0$iso3c)
#d0$a14y        <- factor(d0$a14y)
```
```{r}
vars <- c(
  "lprYL_pp_win","ln_density_win","ln_pop_win","ln_size","ln_age","ln_exp","multi",
  "region_name","sector_MS","iso3c","a14y",
  "w_city_norm","id_city"              # <- make sure both are here
)

mf2 <- droplevels(na.omit(firms_v4[ , vars]))

m_noPop <- lm(
  lprYL_pp_win ~ ln_density_win + ln_size + ln_age + ln_exp + multi +
    factor(region_name) + factor(sector_MS) + factor(iso3c) + factor(a14y),
  data = mf2, weights = w_city_norm, na.action = na.exclude
)

m_withPop <- lm(
  lprYL_pp_win ~ ln_density_win + ln_pop_win + ln_size + ln_age + ln_exp + multi +
    factor(region_name) + factor(sector_MS) + factor(iso3c) + factor(a14y),
  data = mf2, weights = w_city_norm, na.action = na.exclude
)

#library(sandwich); library(lmtest); library(car)
V_pop <- vcovCL(m_withPop, cluster = ~ id_city, type = "HC1") 

car::linearHypothesis(m_withPop, "ln_pop_win = 0", vcov = V_pop, singular.ok = TRUE)
```

# Simple regression firms productivity with density: EMTRENDS (regional trends)
```{r}
mod_lin_byreg <- lm(
  lprYL_pp_win ~ ln_density_win * region_name + ln_size + ln_age + ln_exp + multi+
    sector_MS + iso3c + a14y,
  data = firms_v4, weights = w_city_norm, na.action = na.exclude
)

# Predictions over the observed support of ln_density, by region
pred <- ggpredict(mod_lin_byreg, terms = c("ln_density_win [all]", "region_name"))

# Plot
ggplot(pred, aes(x = x, y = predicted, color = group)) +
  geom_line(size = 1.2) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = group),
              alpha = 0.12, color = NA) +
  labs(
    x = "Log city density (winsorized)",
    y = "Predicted log productivity (sales per worker)",
    color = "Region", fill = "Region",
    title = "Density–productivity trends by region (controls held fixed)"
  ) +
  theme_minimal(base_size = 12)

#ggsave(paste0(dir_out, "graph trends.png"), height = 2.5, width = 4, units = "in")
library(emmeans)
V_lin <- vcovCL(mod_lin_byreg, cluster = ~ id_city, type = "HC1")

# Per-region slopes (elasticities) of ln_density_win
emtr <- emtrends(
  mod_lin_byreg,
  specs = ~ region_name,
  var   = "ln_density_win",
  vcov. = V_lin
) %>% summary(infer = c(TRUE, TRUE))

# Make a neat data frame
slopes <- emtr %>%
  as.data.frame() %>%
  rename(beta = ln_density_win.trend,
         se   = SE,
         lo   = lower.CL,
         hi   = upper.CL,
         p.value= p.value)

# Forest plot
slopes$stars <- cut(slopes$p.value,
                    breaks = c(-Inf, 0.001, 0.01, 0.05, 0.1, Inf),
                    labels = c("***","**","*","+",""))

tree<-ggplot(slopes, aes(x = beta, y = region_name)) +
  geom_point(size = 2) +
  geom_errorbarh(aes(xmin = lo, xmax = hi), height = 0.15) +
  geom_text(aes(label = stars), vjust = -.3, hjust = -1, size = 7) +
  #  geom_text(aes(label = sprintf("p=%.3f", p.value)),
    #        hjust = -0.2, size = 3)+
  geom_vline(xintercept = 0, linetype = 2) +
  labs(
    x = "Elasticity of productivity(In sales per worker) ~ log density",
    y = "",
    title = "Regional elasticities"
  ) +
  theme_set(theme_minimal()+
  theme(axis.text.y = element_text(size = 10), 
                axis.text.x = element_text(size = 8),
                axis.title.x= element_text(size = 8),
        axis.title.y= element_text(size = 10),
        plot.title = element_text(size = 14)))
tree

ggsave(paste0(dir_out, "tree_linear_no_frag_all_firms.png"), plot = tree, height = 2.5, width = 4, units = "in")
```
#Model with lasym 
```{r}
mod_infer1 <- lm(
  lprYL_pp_win ~ ln_density_win + Lasym_inv + ln_size + ln_age + ln_exp + multi + region_name + sector_MS
    #+ln_pop_win
    + iso3c + a14y,
  data = firms_v4,
  weights = w_city_norm,
  na.action = na.exclude
)
cl_vcov <- sandwich::vcovCL(mod_infer1, cluster = ~ id_city, type = "HC1")
coeftest(mod_infer1, vcov = cl_vcov)

# Create modelsummary table
suppressWarnings(
modelsummary(
  list("Log Labor Prod. (sales per worker)" = mod_infer1),
  vcov = cl_vcov,                    # <—— use this, not vcov_iso
  gof_map = c("nobs", "r.squared"),
  coef_omit = "factor(iso3c)|factor(a14y)|factor(region_name)|factor(sector_MS)",
  coef_map = c(
    "ln_density_win"    = "Log Density",
    "Lasym_inv"= "Lasym inverse",
    "ln_pop_win"    = "Log Population", 
    "ln_size" = "Log Firm size",
    "ln_age" = "Log age of establishment",
    "ln_exp" = "Log owners experience", 
    "multi" = "Multi establishment"
  ),
  stars = TRUE,
  title = "lprYL_pp_win ~ ln_density_win +  ln_size + ln_age + ln_pop_win+
    ln_exp + multi + region_name + sector_MS + 
    + iso3c + year",
  fmt = 3,
  output = file.path(dir_out, "model_desity_lasym.html")
))

#### get regional trends 

mod_infer1 <- lm(
  lprYL_pp_win ~ ln_density_win*region_name + Lasym_inv + ln_size + ln_age + ln_exp + multi + sector_MS+ #ln_pop_win+ 
    iso3c + a14y,
  data = firms_v4,
  weights = w_city_norm,
  na.action = na.exclude
)
cl_vcov <- sandwich::vcovCL(mod_infer1, cluster = ~ id_city, type = "HC1")
coeftest(mod_infer1, vcov = cl_vcov)

#Per-region slopes (elasticities) of ln_density_win
emtr <- emtrends(
  mod_infer1,
  specs = ~ region_name,
  var   = "ln_density_win",
  vcov. = cl_vcov 
) %>% summary(infer = c(TRUE, TRUE))

# Make a neat data frame
slopes <- emtr %>%
  as.data.frame() %>%
  rename(beta = ln_density_win.trend,
         se   = SE,
         lo   = lower.CL,
         hi   = upper.CL,
         p.value= p.value)
slopes 
#interaction with lasym
mod_infer1 <- lm(
  lprYL_pp_win ~ ln_density_win*Lasym_inv + ln_size + ln_age + ln_exp + multi + region_name + sector_MS 
   +ln_pop_win 
  +  iso3c + a14y,
  data = firms_v4,
  weights = w_city_norm,
  na.action = na.exclude
)
cl_vcov <- sandwich::vcovCL(mod_infer1, cluster = ~ id_city, type = "HC1")
coeftest(mod_infer1, vcov = cl_vcov)

# Create modelsummary table
suppressWarnings(
modelsummary(
  list("Log Labor Prod. (sales per worker)" = mod_infer1),
  vcov = cl_vcov,                    # <—— use this, not vcov_iso
  gof_map = c("nobs", "r.squared"),
  coef_omit = "factor(iso3c)|factor(a14y)|factor(region_name)|factor(sector_MS)",
  coef_map = c(
    "ln_density_win"    = "Log Density",
    "Lasym_inv"= "Lasym inverse",
    "ln_density_win:Lasym_inv"= "Log density*Lasym inv",
    "ln_pop_win"    = "Log Population", 
    "ln_size" = "Log Firm size",
    "ln_age" = "Log age of establishment",
    "ln_exp" = "Log owners experience", 
    "multi" = "Multi establishment"
  ),
  stars = TRUE,
  title = "lprYL_pp_win ~ ln_density_win*Lasym_inv +  ln_size + ln_age + ln_pop_win+
    ln_exp + multi + region_name + sector_MS + 
    + iso3c + year",
  fmt = 3,
  output = file.path(dir_out, "model_desity_lasym_interv2.html")
))

#interaction lasym and region

mod_infer1 <- lm(
  lprYL_pp_win ~ ln_density_win*Lasym_inv*region_name + ln_size + ln_age + ln_exp + multi + sector_MS+ ln_pop_win+ 
    iso3c + a14y,
  data = firms_v4,
  weights = w_city_norm,
  na.action = na.exclude
)
cl_vcov <- sandwich::vcovCL(mod_infer1, cluster = ~ id_city, type = "HC1")
coeftest(mod_infer1, vcov = cl_vcov)

emtr <- emtrends(
  mod_infer1,
  specs = ~ region_name,
  var   = "ln_density_win",
  vcov. = cl_vcov, 
  nuisance = c("sector_MS", "iso3c", "a14y"),
) %>% summary(infer = c(TRUE, TRUE))
emtr
# Make a neat data frame
slopes <- emtr %>%
  as.data.frame() %>%
  rename(regional_beta = ln_density_win.trend,
         se   = SE,
         lo   = lower.CL,
         hi   = upper.CL,
         p.value= p.value)
slopes 



dens_slopes <- emtrends(
  mod_infer1,
  var = "ln_density_win",
  specs = ~ region_name * Lasym_inv,
  at = list(Lasym_inv = quantile(firms_v4$Lasym_inv, probs = c(0.1, 0.5, 0.9), na.rm = TRUE))
)

summary(dens_slopes, infer = c(TRUE, TRUE))
 #region_name regional_beta        se    df         lo        hi t.ratio p.value
# EAP                    NA        NA    NA         NA        NA      NA      NA
 #LAC             0.7023743 0.2093671 10191  0.2919737 1.1127750   3.355  0.0008
 #SAR            -0.3422273 0.5358064 10191 -1.3925133 0.7080586  -0.639  0.5230
 #SSA            -0.2226588 0.3766278 10191 -0.9609233 0.5156058  -0.591  0.5544
#Results are averaged over the levels of: 3 nuisance factors, multi 
#Confidence level used: 0.95 
```


#Model with Batty 
```{r}
range(firms_v4$Batty, na.rm =T)
firms_v4$batty_z <- scale(firms_v4$Batty)

range(firms5$Batty, na.rm =T)
firms5$batty_z <- scale(firms5$Batty)

mod_infer1 <- lm(
  lprYL_pp_win ~ ln_density_win + batty_z + ln_size + ln_age + ln_exp + multi + region_name + sector_MS
    #+ln_pop_win
    +ln_roads_win
    +iso3c + a14y,
  data = firms_v4,
  weights = w_city_norm,
  na.action = na.exclude
)
cl_vcov <- sandwich::vcovCL(mod_infer1, cluster = ~ id_city, type = "HC1")
coeftest(mod_infer1, vcov = cl_vcov)

# Create modelsummary table
suppressWarnings(
modelsummary(
  list("Log Labor Prod. (sales per worker)" = mod_infer1),
  vcov = cl_vcov,                    # <—— use this, not vcov_iso
  gof_map = c("nobs", "r.squared"),
  coef_omit = "factor(iso3c)|factor(a14y)|factor(region_name)|factor(sector_MS)",
  coef_map = c(
    "ln_density_win"    = "Log Density",
    "batty_z"= "Batty (rescaled)",
    #"Lasym_inv"= "Lasym inverse",
    "ln_roads_win" = "Road Density",
    "ln_pop_win"    = "Log Population", 
    "ln_size" = "Log Firm size",
    "ln_age" = "Log age of establishment",
    "ln_exp" = "Log owners experience", 
    "multi" = "Multi establishment"
  ),
  stars = TRUE,
  title = "lprYL_pp_win ~ ln_density_win +  batty_z+  ln_size + ln_age + 
    ln_exp + multi + region_name + sector_MS 
    + iso3c + year",
  fmt = 3,
  output = file.path(dir_out, "model_desity_batty2.html")
))


#### get regional trends 

mod_infer1 <- lm(
  lprYL_pp_win ~ ln_density_win*region_name + batty_z + ln_size + ln_age + ln_exp + multi + sector_MS #ln_pop_win+
    +ln_pop_win
    +ln_roads_win
    +iso3c + a14y,
  data = firms_v4,
  weights = w_city_norm,
  na.action = na.exclude
)
cl_vcov <- sandwich::vcovCL(mod_infer1, cluster = ~ id_city, type = "HC1")
coeftest(mod_infer1, vcov = cl_vcov)

#Per-region slopes (elasticities) of ln_density_win
emtr <- emtrends(
  mod_infer1,
  specs = ~ region_name,
  var   = "ln_density_win",
  vcov. = cl_vcov 
) %>% summary(infer = c(TRUE, TRUE))
emtr
# Make a neat data frame
#slopes <- emtr %>%
 # as.data.frame() %>%
 # rename(beta = ln_density_win.trend,
 #        se   = SE,
 #        lo   = lower.CL,
 #        hi   = upper.CL,
  #       p.value= p.value)
#slopes 

###########Interaction with batty
mod_infer1 <- lm(
  lprYL_pp_win ~ ln_density_win*batty_z + ln_size + ln_age + ln_exp + multi + region_name + sector_MS #ln_pop_win+ 
  +ln_pop_win
    +ln_roads_win
    +iso3c + a14y,
  data = firms_v4,
  weights = w_city_norm,
  na.action = na.exclude
)
cl_vcov <- sandwich::vcovCL(mod_infer1, cluster = ~ id_city, type = "HC1")
coeftest(mod_infer1, vcov = cl_vcov)

##### Create modelsummary table
suppressWarnings(
modelsummary(
  list("Log Labor Prod. (sales per worker)" = mod_infer1),
  vcov = cl_vcov,                    # <—— use this, not vcov_iso
  gof_map = c("nobs", "r.squared"),
  coef_omit = "factor(iso3c)|factor(a14y)|factor(region_name)|factor(sector_MS)",
  coef_map = c(
    "ln_density_win"    = "Log Density",
    "ln_density_win:batty_z"= "Log Density*Batty (rescaled)",
    #"Lasym_inv"= "Lasym inverse",
    #"ln_pop_win"    = "Log Population", 
    "ln_size" = "Log Firm size",
    "ln_roads_win"= "RoadsIn",
    "ln_age" = "Log age of establishment",
    "ln_exp" = "Log owners experience", 
    "multi" = "Multi establishment"
  ),
  stars = TRUE,
  title = "lprYL_pp_win ~ ln_density_win* batty_z+  ln_size + ln_age + 
    ln_exp + multi + region_name + sector_MS 
    + iso3c + year",
  fmt = 3,
  output = file.path(dir_out, "model_desity_batty_inter.html")
))

#####interaction batty and region

mod_infer1 <- lm(
  lprYL_pp_win ~ ln_density_win*batty_z*region_name + ln_size + ln_age + ln_exp + multi + sector_MS #ln_pop_win+ 
   +ln_pop_win
    +ln_roads_win+  
  iso3c + a14y,
  data = firms_v4,
  weights = w_city_norm,
  na.action = na.exclude
)
cl_vcov <- sandwich::vcovCL(mod_infer1, cluster = ~ id_city, type = "HC1")
coeftest(mod_infer1, vcov = cl_vcov)


emtr <- emtrends(
  mod_infer1,
  specs = ~ region_name,
  var   = "ln_density_win",
  vcov. = cl_vcov, 
  nuisance = c("sector_MS", "iso3c", "a14y"),
) %>% summary(infer = c(TRUE, TRUE))
emtr 

emtr <- emtrends(
  mod_infer1,
  specs = ~ region_name* batty_z,
  var   = "ln_density_win",
  vcov. = cl_vcov, 
   at    = list(batty_z = c(-1, 0, 1)),
  nuisance = c("sector_MS", "iso3c", "a14y"),
) %>% summary(infer = c(TRUE, TRUE))
emtr 


emtr  <- as.data.frame(summary(emtr , infer = c(TRUE, TRUE)))
write.csv(emtr , paste0(dir_out, "batty_z_regions.csv"), row.names = FALSE)
```
#Model with shanon 
```{r}
range(firms_v4$Shannon, na.rm =T)

mod_infer1 <- lm(
  lprYL_pp_win ~ ln_density_win + Shannon + ln_size + ln_age + ln_exp + multi + region_name + sector_MS#+ #ln_pop_win+ 
    #+ln_pop_win
    #+ln_roads_win +
   +iso3c + a14y,
  data = firms_v4,
  weights = w_city_norm,
  na.action = na.exclude
)
cl_vcov <- sandwich::vcovCL(mod_infer1, cluster = ~ id_city, type = "HC1")
coeftest(mod_infer1, vcov = cl_vcov)

# Create modelsummary table
suppressWarnings(
modelsummary(
  list("Log Labor Prod. (sales per worker)" = mod_infer1),
  vcov = cl_vcov,                    # <—— use this, not vcov_iso
  gof_map = c("nobs", "r.squared"),
  coef_omit = "factor(iso3c)|factor(a14y)|factor(region_name)|factor(sector_MS)",
  coef_map = c(
    "ln_density_win"    = "Log Density",
    "Shannon"= "Shannon",
    #"Lasym_inv"= "Lasym inverse",
    #"ln_pop_win"    = "Log Population", 
    "ln_size" = "Log Firm size",
    "ln_age" = "Log age of establishment",
    "ln_exp" = "Log owners experience", 
    "multi" = "Multi establishment"
  ),
  stars = TRUE,
  title = "lprYL_pp_win ~ ln_density_win +  Shannon+  ln_size + ln_age + 
    ln_exp + multi + region_name + sector_MS 
    + iso3c + year",
  fmt = 3,
  output = file.path(dir_out, "model_desity_shannon.html")
))

#### get regional trends 

mod_infer1 <- lm(
  lprYL_pp_win ~ ln_density_win*region_name + Shannon + ln_size + ln_age + ln_exp + multi + sector_MS+ #ln_pop_win+ 
    iso3c + a14y,
  data = firms_v4,
  weights = w_city_norm,
  na.action = na.exclude
)
cl_vcov <- sandwich::vcovCL(mod_infer1, cluster = ~ id_city, type = "HC1")
coeftest(mod_infer1, vcov = cl_vcov)

#Per-region slopes (elasticities) of ln_density_win
emtr <- emtrends(
  mod_infer1,
  specs = ~ region_name,
  var   = "ln_density_win",
  vcov. = cl_vcov 
) %>% summary(infer = c(TRUE, TRUE))
emtr
# Make a neat data frame
#slopes <- emtr %>%
 # as.data.frame() %>%
 # rename(beta = ln_density_win.trend,
 #        se   = SE,
 #        lo   = lower.CL,
 #        hi   = upper.CL,
  #       p.value= p.value)
#slopes 

###########Interaction with shannon
mod_infer1 <- lm(
  lprYL_pp_win ~ ln_density_win*Shannon + ln_size + ln_age + ln_exp + multi + region_name + sector_MS+ #ln_pop_win+ 
    iso3c + a14y,
  data = firms_v4,
  weights = w_city_norm,
  na.action = na.exclude
)
cl_vcov <- sandwich::vcovCL(mod_infer1, cluster = ~ id_city, type = "HC1")
coeftest(mod_infer1, vcov = cl_vcov)

##### Create modelsummary table
suppressWarnings(
modelsummary(
  list("Log Labor Prod. (sales per worker)" = mod_infer1),
  vcov = cl_vcov,                    # <—— use this, not vcov_iso
  gof_map = c("nobs", "r.squared"),
  coef_omit = "factor(iso3c)|factor(a14y)|factor(region_name)|factor(sector_MS)",
  coef_map = c(
    "ln_density_win"    = "Log Density",
    "ln_density_win:Shannon"= "Log Density*Shannon",
    #"Lasym_inv"= "Lasym inverse",
    #"ln_pop_win"    = "Log Population", 
    "ln_size" = "Log Firm size",
    "ln_age" = "Log age of establishment",
    "ln_exp" = "Log owners experience", 
    "multi" = "Multi establishment"
  ),
  stars = TRUE,
  title = "lprYL_pp_win ~ ln_density_win*Shannon+  ln_size + ln_age + 
    ln_exp + multi + region_name + sector_MS 
    + iso3c + year",
  fmt = 3,
  output = file.path(dir_out, "model_desity_shannon_inter.html")
))

#####interaction shannon and region

mod_infer1 <- lm(
  lprYL_pp_win ~ ln_density_win*Shannon*region_name + ln_size + ln_age + ln_exp + multi + sector_MS+ #ln_pop_win+ 
    iso3c + a14y,
  data = firms_v4,
  weights = w_city_norm,
  na.action = na.exclude
)
cl_vcov <- sandwich::vcovCL(mod_infer1, cluster = ~ id_city, type = "HC1")
coeftest(mod_infer1, vcov = cl_vcov)


emtr <- emtrends(
  mod_infer1,
  specs = ~ region_name,
  var   = "ln_density_win",
  vcov. = cl_vcov, 
  nuisance = c("sector_MS", "iso3c", "a14y"),
) %>% summary(infer = c(TRUE, TRUE))
emtr 

emtr <- emtrends(
  mod_infer1,
  specs = ~ region_name*Shannon
  var   = "ln_density_win",
  vcov. = cl_vcov, 
   at    = list(Shannon = c(-1, 0, 1)),
  nuisance = c("sector_MS", "iso3c", "a14y"),
) %>% summary(infer = c(TRUE, TRUE))
emtr 
```


```{r}

mod_quad  <- lm(
  lprYL_pp_win ~ ln_density_win + I(ln_density_win^2) + ln_size + ln_age + ln_exp + multi + region_name + sector_MS+ #ln_pop_win+ 
    iso3c + a14y,
  data = firms_v4,
  weights = w_city_norm,
  na.action = na.exclude
)
cl_vcov <- sandwich::vcovCL(mod_quad, cluster = ~ id_city, type = "HC1")
coeftest(mod_quad, vcov = cl_vcov)


mod_quad_reg  <- lm(
  lprYL_pp_win ~ (ln_density_win + I(ln_density_win^2))*region_name + ln_size + ln_age + ln_exp + multi + region_name + sector_MS+ #ln_pop_win+ 
    iso3c + a14y,
  data = firms_v4,
  weights = w_city_norm,
  na.action = na.exclude
)
cl_vcov <- sandwich::vcovCL(mod_quad_reg , cluster = ~ id_city, type = "HC1")
coeftest(mod_quad_reg , vcov = cl_vcov)


##### Create modelsummary table
suppressWarnings(
modelsummary(
  list("Log Labor Prod. (sales per worker)" = mod_quad),
  vcov = cl_vcov,                    # <—— use this, not vcov_iso
  gof_map = c("nobs", "r.squared"),
  coef_omit = "factor(iso3c)|factor(a14y)|factor(region_name)|factor(sector_MS)",
  coef_map = c(
    "ln_density_win"    = "Log Density",
    "I(ln_density_win^2)"= "Log Densityˆ2",
    #"Lasym_inv"= "Lasym inverse",
    #"ln_pop_win"    = "Log Population", 
    "ln_size" = "Log Firm size",
    "ln_age" = "Log age of establishment",
    "ln_exp" = "Log owners experience", 
    "multi" = "Multi establishment"
  ),
  stars = TRUE,
  title = "lprYL_pp_win ~ ln_density_winI+ (ln_density_win^2)+  ln_size + ln_age + 
    ln_exp + multi + region_name + sector_MS 
    + iso3c + year",
  fmt = 3,
  output = file.path(dir_out, "model_desity_quadratic2.html")
))


mod_quad2  <- lm(
  lprYL_pp_win ~ ln_density_win + I(ln_density_win^2) + ln_size + ln_age + ln_exp + multi + region_name + sector_MS+ ln_pop_win+ 
    iso3c + a14y,
  data = firms_v4,
  weights = w_city_norm,
  na.action = na.exclude
)
cl_vcov <- sandwich::vcovCL(mod_quad2, cluster = ~ id_city, type = "HC1")
coeftest(mod_quad2, vcov = cl_vcov)


##### Create modelsummary table
suppressWarnings(
modelsummary(
  list("Log Labor Prod. (sales per worker)" = mod_quad2),
  vcov = cl_vcov,                    # <—— use this, not vcov_iso
  gof_map = c("nobs", "r.squared"),
  coef_omit = "factor(iso3c)|factor(a14y)|factor(region_name)|factor(sector_MS)",
  coef_map = c(
    "ln_density_win"    = "Log Density",
    "I(ln_density_win^2)"= "Log Densityˆ2",
    #"Lasym_inv"= "Lasym inverse",
    "ln_pop_win"    = "Log Population", 
    "ln_size" = "Log Firm size",
    "ln_age" = "Log age of establishment",
    "ln_exp" = "Log owners experience", 
    "multi" = "Multi establishment"
  ),
  stars = TRUE,
  title = "lprYL_pp_win ~ ln_density_winI+ (ln_density_win^2)+  ln_size + ln_age + In_pop + 
    ln_exp + multi + region_name + sector_MS 
    + iso3c + year",
  fmt = 3,
  output = file.path(dir_out, "model_desity_quadratic_pop.html")
))


#######Quadratic with regional slopes

mod_quad2_region <- lm(
  lprYL_pp_win ~ (ln_density_win + I(ln_density_win^2))*region_name + ln_size + ln_age + ln_exp + multi + sector_MS+ ln_pop_win+ 
    iso3c + a14y,
  data = firms_v4,
  weights = w_city_norm,
  na.action = na.exclude
)
cl_vcov <- sandwich::vcovCL(mod_quad2_region, cluster = ~ id_city, type = "HC1")
coeftest(mod_quad2_region, vcov = cl_vcov)


emtr_quad <- emtrends(
  mod_quad2_region,
  ~ region_name,
  var =  c("ln_density_win"),
  nuisance = c("sector_MS", "iso3c", "a14y"),
  vcov. = cl_vcov)

summary(emtr_quad, infer = c(TRUE, TRUE))

emtr_quad <- emtrends(
  mod_quad2_region,
  ~ region_name,
  var =  c("I(ln_density_win^2)"),
  nuisance = c("sector_MS", "iso3c", "a14y"),
  vcov. = cl_vcov)

summary(emtr_quad, infer = c(TRUE, TRUE))


####get population size 

```

```{r}
pred_curve <- ggpredict(
 mod_quad2_region,
  terms = c("ln_density_win [all]", "region_name")
)

ggplot(pred_curve, aes(x = x, y = predicted, color = group)) +
  geom_line(size = 1.2) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = group),
              alpha = 0.15, color = NA) +
  labs(x = "Log city density",
       y = "Predicted log productivity (sales per worker)",
       color = "Region", fill = "Region",
       title = "Quadratic density–productivity relationship by region") +
  theme_minimal(base_size = 13)

ggsave(paste0(dir_out, "curavature_cuadratic_pop.png"), plot = curve, height = 2.5, width = 4, units = "in")
```
```{r}
grid <- seq(min(firms_v4$ln_density_win, na.rm = TRUE),
            max(firms_v4$ln_density_win, na.rm = TRUE),
            length.out = 40)

emtr_quad <- emtrends(
  mod_quad2_region,
  ~ region_name | ln_density_win,
  var = "ln_density_win",
  at  = list(ln_density_win = grid),
  nuisance = c("sector_MS", "iso3c", "a14y"),
  vcov. = cl_vcov 
)
slopes <- as.data.frame(emtr_quad)

ggplot(slopes, aes(x = ln_density_win, y = ln_density_win.trend, color = region_name)) +
  geom_line(size = 1.1) +
  geom_ribbon(aes(ymin = lower.CL, ymax = upper.CL, fill = region_name),
              alpha = 0.15, color = NA) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Log density",
       y = "Elasticity of productivity w.r.t. density",
       color = "Region", fill = "Region",
       title = "Marginal effect of density by region (quadratic model)") +
  theme_minimal(base_size = 13)
```
```{r}
coefs <- coef(mod_quad2_region)
regions <- levels(firms_v4$region_name)
tp <- sapply(regions, function(r){
  b1 <- coefs[paste0("ln_density_win")]
  b2 <- coefs["I(ln_density_win^2)"]
  if(r != regions[1]) {
    if(paste0("ln_density_win:region_name", r) %in% names(coefs))
      b1 <- b1 + coefs[paste0("ln_density_win:region_name", r)]
    if(paste0("I(ln_density_win^2):region_name", r) %in% names(coefs))
      b2 <- b2 + coefs[paste0("I(ln_density_win^2):region_name", r)]
  }
  data.frame(region = r,
             b1 = b1,
             b2 = b2,
             lnD_star = -b1/(2*b2))
})
tp <- do.call(rbind, tp)
tp$D_star <- exp(tp$lnD_star)
tp
```

#ROADS
```{r}
mod_infer1 <- lm(
  lprYL_pp_win ~ ln_density_win + ln_roads+ ln_size + ln_age + ln_exp + multi + region_name + sector_MS
    #+ln_pop_win
    + iso3c + a14y,
  data = firms_v4,
  weights = w_city_norm,
  na.action = na.exclude
)
cl_vcov <- sandwich::vcovCL(mod_infer1, cluster = ~ id_city, type = "HC1")
coeftest(mod_infer1, vcov = cl_vcov)


mod_infer1 <- lm(
  lprYL_pp_win ~ ln_density_win*ln_roads+ ln_size + ln_age + ln_exp + multi + region_name + sector_MS
    #+ln_pop_win
    + iso3c + a14y,
  data = firms_v4,
  weights = w_city_norm,
  na.action = na.exclude
)
cl_vcov <- sandwich::vcovCL(mod_infer1, cluster = ~ id_city, type = "HC1")
coeftest(mod_infer1, vcov = cl_vcov)

####ROADS INTERACTION 

mod_infer1 <- lm(
  lprYL_pp_win ~ ln_density_win*ln_roads*region_name + ln_size + ln_age + ln_exp + multi + sector_MS+  
    iso3c + a14y,
  data = firms_v4,
  weights = w_city_norm,
  na.action = na.exclude
)
cl_vcov <- sandwich::vcovCL(mod_infer1, cluster = ~ id_city, type = "HC1")
coeftest(mod_infer1, vcov = cl_vcov)

emtr <- emtrends(
  mod_infer1,
  specs = ~ region_name,
  var   = "ln_density_win",
  vcov. = cl_vcov, 
  nuisance = c("sector_MS", "iso3c", "a14y"),
) %>% summary(infer = c(TRUE, TRUE))
emtr



dens_slopes <- emtrends(
  mod_infer1,
  var = "ln_density_win",
  specs = ~ region_name * ln_roads,
  at = list(ln_roads = quantile(firms_v4$ln_roads, probs = c(0.1, 0.5, 0.9), na.rm = TRUE))
)

summary(dens_slopes, infer = c(TRUE, TRUE))
```





